Appendix S1. Linear regression models and non-linear population dynamics

### 2024-09-13 manuscript/Appendix_S1_v01.Rmd
Finished AppS1 all scenarios, knit

@@

```{r warning=FALSE}
VP <- computeVariancePartitioning(m.6.sample,group=c(1,1,1),groupnames="Env")
plotVariancePartitioning(m.6.sample,VP,args.legend=list(cex=0.75,bg="transparent"))
```

>>>>

```{r}
preds = computePredictedValues(m.3.sample)
df <- data.frame(cbind(log(dat$N1[2:t]),log(dat$N2[2:t]),log(dat$N1[1:(t-1)]),log(dat$N2[1:(t-1)])))
colnames(df) <- c("Nt1","Nt2","N1","N2")
df$n1_25 <- NA
df$n1_975 <- NA
df$n2_25 <- NA
df$n2_975 <- NA
for(i in 1:39){
  red <- preds[i,,]
  a <- apply(red,1,quantile,probs=c(.025,.975))
  df$n1_25[i] <- a[1,1]
  df$n1_975[i] <- a[2,1]
  df$n2_25[i] <- a[1,2]
  df$n2_975[i] <- a[2,2]
}
plot(df$Nt1,pch=19,col="black",ylim=c(0,5))
points(df$Nt2,pch=19,col="orange")
lines(df$n1_25,col="black")
lines(df$n1_975,col="black")
lines(df$n2_25,col="orange")
lines(df$n2_975,col="orange")
```

@@

```{r warning=FALSE}
VP <- computeVariancePartitioning(m.6.sample,group=c(1,1,1),groupnames="Env")
plotVariancePartitioning(m.6.sample,VP,args.legend=list(cex=0.75,bg="transparent"))
```
```{r}
preds = computePredictedValues(m.6.sample)
df$n1_25 <- NA
df$n1_975 <- NA
df$n2_25 <- NA
df$n2_975 <- NA
for(i in 1:39){
  red <- preds[i,,]
  a <- apply(red,1,quantile,probs=c(.025,.975))
  df$n1_25[i] <- a[1,1]
  df$n1_975[i] <- a[2,1]
  df$n2_25[i] <- a[1,2]
  df$n2_975[i] <- a[2,2]
}
plot(df$Nt1,pch=19,col="black",ylim=c(0,5))
points(df$Nt2,pch=19,col="orange")
lines(df$n1_25,col="black")
lines(df$n1_975,col="black")
lines(df$n2_25,col="orange")
lines(df$n2_975,col="orange")
```
